Abstract

### 2025-01-23 output/Main_text.Rmd
Correct use of curly double quote characters

On an unrelated basis, negative loadings/discrimination parameters
are often irrelevant in MIRT applications in the cognitive testing domain.
It has been argued that discrimination parameters
"are constrained to be positive" [@ackerman_graphical_1996, p. 315],
or that “in an [independent-clusters] solution, the loadings can always
be selected to be positive” [@mcdonald_basis_2000, p. 110].
However, when such instances of negative parameters appear,
they are often dismissed as “particularly puzzling” (p. 109),
or implicitly assuming item malfunctioning without further discussion
[e.g., @ackerman_multidimensional_2005-1].
In the non-cognitive domain though, the use of so-called negatively-keyed items
---items that tap the negative pole of a certain trait, and thus
usually reverse-scored--- is widespread
[consider, e.g., the statement "Neglect my duties" in the Conscientiousness item
of the Big-Five Factor Markers, @noauthor_international_nodate].
Instruments that combine positively- and negatively-keyed items
are relatively common, and
complex indicators may even have discrimination parameters
with opposite signs for different latent dimensions
[see, e.g., @mclarnon_be_2016,
for item parcels with both positive and negative loadings,
on method factors in the case of the negative ones].
Following @ackerman_multidimensional_2005-1, one can easily note that
a monotonically decreasing probability for a certain dimension
is given by a non-positive discrimination parameter
(and an unchanging probability by a null discrimination parameter,
which also applies to cognitive instruments),
contrary to the constraints imposed by @reckase_difficulty_1985 [p. 411]
for determining the multidimensional difficulty.
However, the multidimensional item parameters can also be defined for
items with monotonically non-increasing probabilities, as we will see.

>>>>

On an unrelated basis, negative loadings/discrimination parameters
are often irrelevant in MIRT applications in the cognitive testing domain.
It has been argued that discrimination parameters
"are constrained to be positive" [@ackerman_graphical_1996, p. 315],
or that "in an [independent-clusters] solution, the loadings can always
be selected to be positive" [@mcdonald_basis_2000, p. 110].
However, when such instances of negative parameters appear,
they are often dismissed as "particularly puzzling" (p. 109),
or implicitly assuming item malfunctioning without further discussion
[e.g., @ackerman_multidimensional_2005-1].
In the non-cognitive domain though, the use of so-called negatively-keyed items
---items that tap the negative pole of a certain trait, and thus
usually reverse-scored--- is widespread
[consider, e.g., the statement "Neglect my duties" in the Conscientiousness item
of the Big-Five Factor Markers, @noauthor_international_nodate].
Instruments that combine positively- and negatively-keyed items
are relatively common, and
complex indicators may even have discrimination parameters
with opposite signs for different latent dimensions
[see, e.g., @mclarnon_be_2016,
for item parcels with both positive and negative loadings,
on method factors in the case of the negative ones].
Following @ackerman_multidimensional_2005-1, one can easily note that
a monotonically decreasing probability for a certain dimension
is given by a non-positive discrimination parameter
(and an unchanging probability by a null discrimination parameter,
which also applies to cognitive instruments),
contrary to the constraints imposed by @reckase_difficulty_1985 [p. 411]
for determining the multidimensional difficulty.
However, the multidimensional item parameters can also be defined for
items with monotonically non-increasing probabilities, as we will see.
